Data Exploration

### 2019-02-20 src/data_exploration.Rmd
playing with patterns and stack creation for prediction layers

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
p
testmax <- maxent(janpresmax, janabmax)
```

>>>>

loop creating layer stacks
```{r}
jan98_86.9 <- stack(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*_86.9294*.asc"), full.names = TRUE))    # this folder currently contains other dummy files. its just a test to automate stacks
names(jan98_86.9) # now need to rename to match maxent expectations
names(jan98_86.9) <- (pattern = "*chl_surface*" paste0("chl_surface"))
```

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')

testmax <- maxent(janpresabmax, janpresabmax$occurrence)
